
\documentclass[10pt]{article}


\usepackage{array}
\usepackage{xspace}

\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}

\usepackage{url}
\usepackage{subfig}
\usepackage{paralist}
\usepackage{afterpage}
\usepackage{wrapfig}

\usepackage{calc}

\usepackage[margin=0.5in]{geometry}


\input{results}
\input{definitions}

\begin{document}


\title{\Leap results}


\maketitle


This document describes the results we have obtained applying \Leap to a set of 
examples. The results are divided into two sections. The first section presents 
the sequential examples, mainly based on skiplists. The second section presents 
the concurrent examples based on a ticketing system and lock-coupling lists.

Each section presents two tables. The first table describes each invariant 
candidate and the decision procedures used in order to verify them. The second 
table presents the required analysis time for each invariant candidate.

Consider the first table of each section. When dealing with concurrency, we say 
that a parametrized formula is a formula parametrized by some thread 
identifiers. The number of thread identifiers parametrizing an invariant 
candidate is what we call the \emph{index} of the formula. This number is shown 
in the second column of the tables.

Depending on the proof rules we apply (\binv, \pinv, \spinv, ...) and the length 
of the program, a number of verification conditions (VCs) are generated.  The 
number of generated VCs that needs to be verified as valid for each invariant 
candidate is shown in the third column. A feature of \Leap is the possibility of 
applying tactics in order to simplify VCs. Applying a tactic on a single VC may 
simplify it, or it may produce many new VCs that subsumes the original VC.  
However, the idea is that all new VCs obtained through the application of 
tactics are simpler to analyze than the original one. Thus, the number of actual 
final VCs (or queries as we call them) passed to the solvers may be more than 
the original number of VCs. The number of final queries is depicted in the forth 
column of the table.

The final eight columns of the table contain the number of calls performed to 
each decision procedure in order to solve all the queries. We use the following 
decision procedures:

\begin{itemize}
\item A \FODP decision procedure, which reasons only about first order logic and 
information regarding the program counter. This DP usually solves simple queries 
in almost no time, speeding up the verification process.
\item A \NumDP decision procedure, which is capable of reasoning about 
Presburger Arithmetic with sets of integers.
\item A \TLLDP decision procedure, capable of dealing with concurrent 
lock-coupling single-linked lists.
\item A \TSLDP decision procedure, which deals with skiplists of arbitrary 
height.
\item A set of \TSLKOneDP, \TSLKTwoDP, \TSLKThreeDP and \TSLKFourDP decision 
procedures, capable of reasoning about skiplists with a fixed number of levels 
($1$, $2$, $3$ and $4$ respectively).
\end{itemize}

In all cases not involving the use of \TSLDP, the sum of calls performed to all 
decision procedures is equal to the number of generated queries. On the other 
hand, in the case of the skiplist example involving \TSLDP, notice that only the 
sum of calls performed to \FODP and \TSLDP is equal to the number of generated 
queries. This means that each query is solved through first order logic 
reasoning or, if not possible, through a call to the \TSLDP decision procedure.  
However, because of how \TSLDP decision procedure works, a single call to \TSLDP 
may require multiple calls to \NumDP (when guessing arrangements) as well as to 
simpler decision procedures such as \TSLKOneDP, \TSLKTwoDP, \TSLKThreeDP and 
\TSLKFourDP.

Now, consider the second table on each section. These tables show the time 
required in order to analyze all generated VCs for each invariant candidate.  
The first column presents the name of the invariant candidate. The second column 
depicts the number of generated VCs (which matches with the first table). Then, 
we present three columns showing the least, most and average time it takes to 
analyze a single VC. The sixth column shows the total time employed by the 
decision procedures to analyze all VCs. The final column presents the total time 
required by \Leap in order to completely analyze and verify the invariant 
candidate. This value is greater than the one shown in the previous column as it 
includes, in addition to the time employed by the decision procedures, the time 
required to parse the program, the invariant candidates, generate the VCs, apply 
tactics, transform the intermediate formulas, etc. All the times shown in these 
tables are in seconds.


\section{Sequential examples}

\ResultsSequentialInfo

\vspace{3em}

\ResultsSequentialTimes

\pagebreak

\section{Concurrent examples}

\ResultsConcurrentInfo

\vspace{3em}

\ResultsConcurrentTimes

\end{document}


%%% Local Variables:
%%% TeX-PDF-mode: t
%%% End:
